Hartree-Fock Stability

### 2016-09-30 presentations/GroupMeeting_Fall2016.tex
Added images, image generator and a unimportant things. Also added group meeting stuff

\usetheme{metropolis}
\usepackage{appendixnumberbeamer}

\usepackage{booktabs}
\usepackage[scale=2]{ccicons}

@@

\title{Hartree-Fock Stability}
\subtitle{Applications to the Homogeneous Electron Gas}
\date{\today}
\author{Evan Curtin}
\institute{University of Illinois at Urbana-Champaign}
% \titlegraphic{\hfill\includegraphics[height=1.5cm]{logo.pdf}}

@@

			General \rule{0pt}{7ex}&
			\begin{tabular}{r@{}r@{}}  
				$\chi_j(\vec{r},\sigma) = \sum\limits_{i=1}^{N} [
				c_{ij}^\alpha\phi_i\left(\vec{r \,}\right) \alpha(\sigma) $
				\\ \rule{0pt}{4ex}
				$+c_{ij}^\beta \phi_i(\vec{r \,}) \beta(\sigma)]  $
			\end{tabular} 
			& 2N & Neither \\ [5ex]

			\hline
		\end{tabular}
	\end{center}

\end{frame}
\begin{frame}[fragile]{Restricted Minimization}
	\includegraphics[width=0.7\linewidth]{../images/pes.jpeg}
\end{frame}

>>>>

\usetheme{metropolis}
\usepackage{appendixnumberbeamer}
\usepackage{graphicx}
\usepackage{booktabs}
\usepackage[scale=2]{ccicons}

@@

\title{Hartree-Fock Stability}
\subtitle{Applications to the Homogeneous Electron Gas}
\date{\today}
\author{Evan Curtin}
\institute{University of Illinois at Urbana-Champaign}
\titlegraphic{\hfill\includegraphics[height=1.5cm]{../images/imark_bold.eps}}

@@

			General \rule{0pt}{7ex}&
			\begin{tabular}{r@{}r@{}}  
				$\chi_j(\vec{r},\sigma) = \sum\limits_{i=1}^{N} [
				c_{ij}^\alpha\phi_i\left(\vec{r \,}\right) \alpha(\sigma) $
				\\ \rule{0pt}{4ex}
				$+c_{ij}^\beta \phi_i(\vec{r \,}) \beta(\sigma)]  $
			\end{tabular} 
			& 2N & Neither \\ [5ex]
			\hline			
		\end{tabular}
	\end{center}
\end{frame}

\begin{frame}[fragile]{Restricted Minimization}
	\begin{itemize}
		\item<1-> Hartee-Fock SCF guarantees only stationary energy w.r.t. change in orbitals
		\item<1-> The solution may be a maximum, minimum or saddle point
		\begin{itemize}
			\item<2-> \emph{Within the constrained space}
		\end{itemize}
	\end{itemize}
	\begin{center}
		\includegraphics[width=0.5\textwidth, trim={3cm, 2cm, 3cm, 2cm}, clip]{../images/1d_extrema.pdf}
	\end{center}
\end{frame}

\begin{frame}[fragile]{Restricted Minimization}
	\includegraphics[width=0.5\linewidth, trim={7cm, 2cm, 7cm, 3cm}, clip]{../images/const_opt_globalmin.jpeg}
\end{frame}

\begin{frame}[fragile]{Restricted Minimization}
	\includegraphics[width=0.5\linewidth, trim={7cm, 2cm, 7cm, 3cm}, clip]{../images/const_opt_saddle.jpeg}
\end{frame}

\begin{frame}[fragile]{Restricted Minimization}
	\includegraphics[width=0.5\linewidth, trim={7cm, 2cm, 7cm, 3cm}, clip]{../images/const_opt_nonstationary.jpeg}
\end{frame}
